Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
line formatting

Recent analyses suggest a general threshold of ~17% live coral cover in the case of
the GBR [@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of
processes; (2) the variety of approaches that could be used to measure those processes; and
(3) the uncertainty surrounding these, it would be unreasonable to assume all
reefs adhere to a single precise $\beta_{0}$ value. Concurrently, it is difficult to
ascertain a suitable $\beta_{0}$ value for each individual reef.

@@

<!-- Split and move below to results/discussion -->
The distribution of number of years above carbonate-cover thresholds is right-skewed, with
many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
levels and natural log total connectivity strength levels follow right-skewed
distributions. Therefore, we analyse the correlation between number of years above
carbonate-cover thresholds and these characteristics using Spearman's correlation
coefficient.

>>>>

Recent analyses suggest a general threshold of \~17% live coral cover in the case of the GBR
[@desbiens]. Given in situ carbonate budgets are influenced by (1) a range of processes; (2)
the variety of approaches that could be used to measure those processes; and (3) the
uncertainty surrounding these, it would be unreasonable to assume all reefs adhere to a
single precise $\beta_{0}$ value. Concurrently, it is difficult to ascertain a suitable
$\beta_{0}$ value for each individual reef.

@@

<!-- Split and move below to results/discussion -->

The distribution of number of years above carbonate-cover thresholds is right-skewed, with
many reefs experiencing low numbers of years above thresholds. Similarly, reef median depth
levels and natural log total connectivity strength levels follow right-skewed distributions.
Therefore, we analyse the correlation between number of years above carbonate-cover
thresholds and these characteristics using Spearman's correlation coefficient.
